---
title: "Interactive Layers on ggplot2"
author: "Michael C Sachs"
date: "September 7, 2017"
output: 
  html_document: 
    self_contained: no
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, dpi = 72, fig.width = 6, fig.height = .618 * 6)

```



```{r mtcars}
library(gginteractive)

p1 <- ggplot(mtcars, aes(x = wt, y = mpg)) + geom_point()
```

A normal ggplot. Next we pipe to a "mesh" layer that allows the viewer to interact with the radio buttons. 


```{r mest2, results = "asis"}
p1 %>% mesh_alpha(geom = "point", variable = "cyl", on = radio)
```


The ggplot object is converted to svg, and interactive elements created with some javascript that is created on the fly. 

Just create a blank mesh, so that the plot is rendered as svg. In Rstudio this will appear in the viewer, rather than the plot window. 

```{r mesh3, results = "asis"}
p1 %>% mesh_blank()
```




The gapminder example: 


```{r gap1, results = "asis"}
library(gapminder)

p2 <- ggplot(gapminder, aes(x = gdpPercap, y = lifeExp, color = continent, size = pop)) +
         geom_point()  + scale_x_log10() 

p2 <- p2 %>% mesh_alpha(geom = "point", variable = "year", on = radio)
p2
```


Convert back to a regular ggplot object: 


```{r}
p2 %>% unmesh()
```



Another example: 


```{r, results = "asis"}
(ggplot(gapminder, aes(x = gdpPercap, y = lifeExp, color = continent, size = pop)) +
   geom_point()  + scale_x_log10()) %>%
  mesh_alpha(geom = "point", variable = "continent", on = radio)
```


Kind of works for other geoms: 

```{r, results = "asis"}
mtcars$cyl2 <- paste(mtcars$cyl)
(ggplot(mtcars, aes(x = wt, y = mpg, color = cyl2)) + geom_bar(stat = "identity")) %>%
  mesh_alpha(geom = "bar", variable = "cyl2", on = radio)
```




